Dummy classifier

### 2020-11-09 src/dummy_classifier.Rmd
Use logistic function in the dummy classifier

---
title: "Dummy classifier"
author: "Jarkko Toivonen"
date: "11/4/2020"
output: html_document
---

@@

source("economic_effect_functions.R")
```

@@

@@

logistic <- function(x) 1 / (1 + exp(-x))

dummy_predictor <- function(df, Hb_threshold=NULL) {
  if (is.null(Hb_threshold)) {
    result <- tibble(Deferred = -df$previous_Hb,
                     obs = df$Hb_deferral)
  } else {
    result <- tibble(Deferred = logistic(-(df$previous_Hb - Hb_threshold)), 
                     obs = df$Hb_deferral)

@@

@@

>>>>

---
title: "Dummy classifier"
author: "Jarkko Toivonen"
date: "11/4/2020"
output: md_document
---

@@

library(tidyverse)
source("economic_effect_functions.R")
source('../../Hb_predictor_container/src/validate_stan_fit.R', chdir=T)
```

@@

We use [Logistic function](https://en.wikipedia.org/wiki/Logistic_function) to map previous_Hb values to
the probability range [0, 1].

@@

logistic <- function(x, k=1, x0=0) 1 / (1 + exp(-k*(x-x0)))

score <- function(previous_Hb, Hb_threshold ) {
  logistic(previous_Hb, k=-0.1, x0=Hb_threshold)
}

make_threshold_conversion_data_frame <- function(Hb_threshold, k) {
  hb <- seq(110, 160, by=2)
  df <- tibble(Hb=hb, 
               Probability = logistic(hb, k=k, x0=Hb_threshold))
  return(df)
}

dummy_predictor <- function(df, Hb_threshold=NULL) {
  if (is.null(Hb_threshold)) {    # use -previous_Hb as score
    result <- tibble(Deferred = -df$previous_Hb,
                     obs = df$Hb_deferral)
  } else {                        # use logistic function of previous_Hb as score
    result <- tibble(Deferred = score(df$previous_Hb, Hb_threshold), 
                     obs = df$Hb_deferral)

@@

```{r}
df1 <- make_threshold_conversion_data_frame(125, -1) 
df2 <- make_threshold_conversion_data_frame(125, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Female")
```

```{r}
df1 <- make_threshold_conversion_data_frame(135, -1) 
df2 <- make_threshold_conversion_data_frame(135, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Male")
```

@@

```{r}
roc_female <- roc_wrapper(prediction_female)
pr_female <- pr_wrapper(prediction_female)
```

```{r}
roc_male <- roc_wrapper(prediction_male)
pr_male <- pr_wrapper(prediction_male)
```

```{r}
v <- c(roc_female$roc$ci[c(2,1,3)], pr_female$ci[c(1,2,3)], 
       roc_male$roc$ci[c(2,1,3)], pr_male$ci[c(1,2,3)])
aucs <- as_tibble(matrix(v, ncol=6, byrow=TRUE))
colnames(aucs) <- c("AUROC", "AUROC low", "AUROC high", "AUPR value", "AUPR low", "AUPR high")
aucs <- aucs %>% 
  mutate(Id=dummy2_ids) %>%
  select(Id, everything())

aucs
```

```{r}
dummy_result <- inner_join(aucs, dummy_result, by="Id")
dummy_result
```
